---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ANSM5

<!-- badges: start -->
<!-- badges: end -->

The ANSM5 package provides a number of functions to accompany the book `Applied Nonparametric Statistical Methods` (5th edition), the revisions from the 4th edition including a move from describing the output from a miscellany of statistical software packages to using R. While the output from many of the functions can also be obtained using a range of pre-existing R functions, this package provides functions in a unified setting and give output using both p-values and confidence intervals, exemplifying the book's approach of treating p-values as a guide to statistical importance and not an end product in their own right.

## Installation

You can install the development version of ANSM5 like so:

``` r
# install.packages("devtools")
devtools::install_github("neilhspencer/ANSM5")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ANSM5)

#From Example 3.1 in `Applied Nonparametric Statistical Methods` (5th edition)
sgn.test(ch3$sampleI, 110)

#From Example 6.1 in `Applied Nonparametric Statistical Methods` (5th edition)
wilcoxon.mann.whitney(ch6$groupA, ch6$groupB)

#From Example 7.6 in `Applied Nonparametric Statistical Methods` (5th edition)
friedman(ch7$pulse, ch7$time.period, ch7$student)
```
